### 2016-06-25 sec6_experiment.tex
A new draft
Flighting

\section{Experimental Study}
\label{sec:exp}
In this section, we present our experimental findings on
deploying our GCMP detectors to large-scaled real trajectories.
All algorithms are were implemented in Java 1.7., and all the 
experiments are carried out on our in-house cluster: Dianwei. The cluster
includes 12 nodes, each of which is equipped with four quad-core 2.2GHz Intel processors,
32 GB memory and gigabit Ethernet. The cluster is installed with CentOS 5.5. 
operating system and Java 1.7.0 VM.

\textbf{Experiment Setup}: We use Yarn\footnote{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html}
to manage the cluster. One node is dedicated as Yarn's master node, and each other node reserves one core and 2 GB memory for
Yarn processes. We use Apache Spark~\cite{zaharia2012resilient} as the MapReduce framework. Spark takes
the remaining 11 nodes as the computing nodes.
To fully utilize the computing power of the cluster, 
we assign each node to run five executors, each executor takes three cores and 5 GB memory. We use "yarn-cluster" mode
for Spark which randomly picks one executor to act as the Application Master. Such a configuration allows us to run 162 tasks
at the same time. We use HDFS as our storage engine with replicator factor of 1.
The configurations of important parameters are summaries in the table below:

%\subsection{Implementation Issues}
%We use Apache Spark~\footnote{http://spark.apache.org/} as the experimental
%platform. Spark is one of the most popular MapReduce platform which
%uses in-memory cache to gain high speedup against Apache Hadoop~\cite{}. 
%Due to the direct support of MapReduce, our algorithm can be easily implemented in Spark. 
%In order to help reproduce our experiments, we further address some implementation issues.
%\subsubsection{Task Assignment}
%In spark, each task in reduce phase is an Apriori mining phase of 
%a star.
%Although our star partition method is theoretically balanced, 
%it is still necessary to assign equal number of tasks to each executors. 
%Spark naturally uses hashing to partition data into tasks, where such
%a partitioning does not care on the tasks size. In order to
%fully utilize the clusters, it is important to perform a weight-aware
%partition. In our implementation, we collect the number of edges
%in each star after map phase. Afterwards, we use a simple \emph{best-fit} strategy,
%where we assign stars in decreasing order with their sizes and each star
%is assigned to the currently least-loaded executor.  HERE WE MAY HAVE ANOTHER BOUND
%FROM LITERATURE, BUT I DIDN'T FIND YET. The injection of load balancing strategy
%between map and reduce phase can be naturally implemented in Spark, where the 
%map result can be cached and the reduce phase can be paused until when the
%partition strategy is ready.
%
%\subsubsection{Duplication Detection}
%It is notable that the patterns discovered from different tasks (stars) could
%be redundant due to containment relationship. For example, a pattern $\{a,b,c\}$
%can be discovered from the star $Sr_a$, while the pattern $\{b,c\}$ can be discovered
%from the star $Sr_b$. Though in most applications, such a duplicate pattern
%is permitted, we offer an option to eliminate these patterns. The strategy is 
%to broadcast each reducers output to every other reducers. This can be
%efficiently done via \emph{broadcast} variables~\footnote{http://spark.apache.org/docs/latest/programming-guide.html\#broadcast-variables} in Spark. Afterwards, each reduce can check 
%whether any resulted patterns are subsumed and thus filter those patterns.
%Theoretically, advanced techniques, such as Bloom Filters, can be applied to efficiently
%deal with the duplication detection. However, as the number of final patterns are
%normally quit small, we leave the exploration for those techniques to the future.
%
%\subsubsection{Handling Overlapping Clusters}
%When handling patterns such as \emph{flock} and \emph{group}, disk-based clustering
%on objects are applied. Such a clustering method may result one object belonging to
%multiple clusters. In such a case, just keeping the timestamps in the edge
%of connection graph is insufficient. Instead, we extend every timestemp $t$
%to a pair $\langle t,C \rangle$, where $C$ is the set of clusters objects
%belong to at time $t$. The only adaption we need to take the join during
%apriori phase. Given two timestamp set $T_1$ and $T_2$, the join result of
%$T_1$ and $T_2$ instead of being $\{\forall t | t\in T_1 \wedge t_\in T_2\}$,
%it changes to $\{\forall (t,C) | t\in T_1 \wedge t \in T_2 \wedge C = (T_1.C \cap T_2.C) \wedge C \neq \emptyset\}$.
%It is obvious to see the \emph{edge simplification} and \emph{candidate pruning} 
%still holds under this new setting.
%
%
%\subsection{Experimental Setup}
%We adapt one of the most popular MapReduce platform, Apache Spark, 
%to conduct experiments on mining GCMPs. 
%Our experiments run on a 9-node cluster, with Apache Yarn as
%the cluster manager. We use 1 node for Yarn resource manager, 
%and use the remaining 8 nodes as executors. Each node in the cluster
%is uniformly equipped with a 2.2GHz quad-core CPU with 32 GB memory. 
%Inter-node communication is carried by 
%the 1Gbps Ethernet.  Some critical configuration of Spark is 
%as follows:
\begin{table} [h]
\centering
\begin{tabular}{|l|c|}
\hline 
Parameter & Value  \\ 
\hline 
Java Version & 1.7.0 \\ 
\hline 
spark.driver.memory & 2GB \\ 
\hline 
spark.executor.cores & 3  \\ 
\hline 
spark.executor.instances & 54 \\ 
\hline 
spark.executor.memory & 5GB \\ 
\hline 
spark.master & yarn-cluster \\
\hline 
spark.serializer & KryoSerializer \\ 
\hline 
\end{tabular} 
\end{table}

\textbf{Datasets}: We prepare three real datasets for study. The details of the datasets are as follows:
\begin{itemize}
\item{Geolife}~\footnote{http://research.microsoft.com/en-us/projects/geolife/}: this dataset collects 
18,670 trajectories for passengers in Beijing over three years. The data are collected
per around 5 seconds. Each data point records a trajectory ID and the latitude/longitude information.
\item{Shopping}~\footnote{http://www.irc.atr.jp/crest2010\_HRI/ATC\_dataset/}: this dataset contains
 visitors trajectories in ATC shopping center in Osaka. The samples are taken per
 around 0.5 seconds. There are in total 13,183 trajectories. Each data point is a 
 trajectory ID with in-door coordinates.
\item{Taxi}: this dataset records 15,054 Singapore taxi trajectories over one month span. The sample 
rate is around 30 seconds. Each data point is the taxi plate with latitude/longitude.
\end{itemize}

\textbf{Preprocessing}: We replace timestamps with a global sequence for each dataset. The sequence number
$0$ is the earliest timestamp among all trajectories in a dataset. We use the sampling rate of 
each dataset as the tick of the sequence number and every data point is mapped to the nearest ticks. If
several points mapped to the same tick, they are merged by averaging the location coordinates.
For missing data within small intervals (i.e., sequence difference less than 10), 
we use linear interpolation to fill them. 
We then use DBSCAN ($\epsilon=5, minPt=10$ for GeoLife and Shopping, $\epsilon=20, minPt=10$ for Taxi)
as the clustering algorithm for preprocessing.  
Note that both our TRPM and SPARSE algorithms treat the preprocessing as a black box and other
spatial clustering methods are also applicable. The clustered snapshots are stored in HDFS in $\langle t, S_t \rangle$ pair, where
$t$ is the timestamp, $S_t$ contains the clusters at snapshot $t$. 
After preprocessing, the summary of statistics are presented as in Table~\ref{exp:dataset}. 
%But they are affected by the number of clusters at each snapshot. We measure the 
%effect of different clustering parameters later.

@@

\textbf{Parameters}: We study the performance of 
the GCMP detectors under various conditions. The variables
to be tested and their value ranges are listed in Table~\ref{tbl:parameters}. 
The default values are highlighted in bold.
\begin{table}[h]
\small
\begin{tabular}{c|l|l}
\hline 
\textbf{Variables} & \textbf{Meaning} & \textbf{Values} \\ 
\hline 
M & min size of object set &  5, 10,  \textbf{15}, 20, 25 \\ 
\hline 
K & min duration & 120, 150, \textbf{180}, 210, 240 \\ 
\hline 
L & min local duration & 10, 20, \textbf{30}, 40,50 \\ 
\hline 
G & max gap & 10, 15, \textbf{20}, 25, 30 \\ 
\hline
N & number of executors & 1, 14, 24, 34, 44, \textbf{54}\\ 
\hline 
\end{tabular} 
\caption{Variables and their default values during experiments.}
\label{tbl:parameters}
\end{table}

\textbf{Algorithms}: We implement TRPM, SPARE and SPARE-LB for comparison study. TRPM and SPARE are implement as described in Section 4 and 5. SPARE-LB extends SPARE by appending an additional load balance stage to the map phase. 
When the mapers complete, SPARE-LB collects the size of stars from all mappers. 
Then the best-fit strategy is applied for task allocation. In best-fit, 
tasks are assigned in decreasing order of their sizes, and the biggest 
unassigned task is allocated to the current mostly empty reducer. 
In SPARE-LB, we simply use the edge size of stars as an estimation of tasks. The other
part of SPARE-LB is identical with SPARE.

\textbf{Number of patterns under different parameters}: Figures~\ref{exp:patterns_vary} presents
 the number of valid GCMP patterns exist in the three datasets. Since the $M$,$K$,$L$,$G$
 impose different constraints on the patterns, the number of valid patterns changes as their 
 values change. We observe that $L$ has a great initial impact on the number of patterns
 discovered. As $L$ increases from $10$ to $20$, the number of patterns drops 50\%. As $L$
 increases further, the number of patterns decreases slowly. Opposed to $L$, when $G$
 is small, the number of patterns increases slowly. As $G$ reaches $30$, 
 the number of patterns nearly doubles. The distribution of patterns under $G$ and $L$
 reveals that there are many companions in real life which are short and repetitive. We can
 either discover these patterns by adjusting property $L$ and $G$ in the GCMP model.

\begin{figure}[h]
\centering
 	 \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_M.eps}
        \caption{Number of patterns vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_K.eps}
        \caption{Number of patterns vary $K$}
    \end{subfigure}  
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_L.eps}
        \caption{Number of patterns vary $L$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_G.eps}
        \caption{Number of patterns vary $G$}
    \end{subfigure}    
\caption{Number of patterns discovered in three datasets on different parameters}
\label{exp:patterns_vary}
\end{figure}

@@

\subsection{Performance Comparison}
Since the both TRPM and SPARE utilizes pruning rules that related to the 
pattern parameters $M$,$L$,$G$,$K$. It is interesting to
see the performance of TRPM and SPARE under different parameter settings.
%\textbf{Default Setting}: We now analyze the TRPM and SPARE algorithm under different
%parameter settings. Under the default parameter settings,
%the performance of TRPM and SPARE is shown as in the 
%following table:
%\begin{table}
%\small
%\begin{tabular}{|c|c|c|c|c|c|c|}
%\hline 
%Data Set& \multicolumn{2}{c|}{TRPM} & \multicolumn{2}{c|}{SPARE} & \# Patterns \\ 
%\hline 
% & Map-Shuffle & Reduce & Map-Shuffle & Reduce &  \\ 
%\hline 			
%Shopping &55 & 279 & 183 &414 &369\\ 
%\hline
%GeoLife &72 & 408 & 162 &585 &441  \\
%\hline
%Taxi &193 & 619 & 562 &3086 &585 \\
%\hline 
%\end{tabular} 
%\caption{Detail performance of TRPM and SPARE under default parameters.}
%\end{table}
%
%As can be seen from the above table, the number of patterns
%discovered by the default parameters are up to five hundreds.
%Thus, the parameter settings are reasonable. Besides, we 
%can see that TRPM suffers from shuffle and mining process. 
%This is because $\eta$ is set to be $309$ under default parameters.
%As a comparison, SPARE takes only in average
% 36\% of TRPM's shuffle time. 
%To study the performance of TRMP and SPARE, we run both algorithms 
%in all three datasets under different parameter settings. 
We run both of the two algorithms in all three dataset and report
their overall performances as in Figures~\ref{exp:performance_vary}.
In brief, both algorithms are able to handle the large-scaled real
datasets. However, we observe that TRMP's performance largely depends
on the pattern parameters. In cases when $G$ is large, 
TRMP takes near three hours (e.g., in Taxi dataset).
In contrast, SPARE performs quite stable. Another general observation
is that both algorithms run slower in the Taxi dataset as compared to
other two datasets. This is because Taxi dataset contains
the most number of temporal data points, which is around 7 times of Shopping
dataset and 5 times of geolife dataset. We observe that, 
in almost all cases, SPARE outperforms TRMP and analyze the detail
of each scenario separately.

@@

    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_M.eps}
        \caption{Taxi vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_K.eps}
        \caption{Taxi vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_L.eps}
        \caption{Taxi vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_G.eps}
        \caption{Taxi vary $G$}
    \end{subfigure}       
\caption{Performance of SPARE and TRPM on real datasets under different pattern parameters.}
\label{exp:performance_vary}
\end{figure*}

\subsubsection{Effects of pattern parameters M,L,K,G}
\textbf{Vary $M$}: Figures~\ref{exp:performance_vary} (a),(e),(i)
present the performance of TRPM and SPARE when $M$ changes under three datasets.
As the figures show, SPARE runs much faster than TRPM. We can see that SPARE
speeds up TRPM 2.7 times in Shopping data, 3.1 times in Geolife data and
7 times in Taxi data. Another observation is that, the running times
of both algorithms slightly decrease as $M$ grows. This is
because when $M$ becomes bigger, smaller clusters (stars) in 
the reduce phase of TRPM and SPARE can be directly pruned.

\textbf{Vary $K$}: Figure~\ref{exp:performance_vary} (b),(f),(j) 
presents the performance of TRPM and SPARE when $K$ changes under three datasets. 
There are two interesting findings in study the performance wrt. $K$. 
First, SPARE and TRPM takes different trends as $K$ increases. 
Whe $K$ increases, SPARE tends to have faster performances 
while TRPM's performances continuously slow down. For SPARE, the 
good performances result from more pruning powers brought
by $K$. When $K$ increases, many shorter time sequences in the reduce phase
are pruned. In contrast, $K$ does not bring much pruning power
during the reduce phase of TRPM. Even $K$ is very large, each reducers in TRPM
still has to sweep the entire partition to determine whether a pattern exists.
Moreover, $\eta$ in TRPM grows linearly with $K$. This indicates that
more data are shuffled and more snapshots are need to
be swept in each partition. This explains the low performance of TRPM as $K$
increases. Another interesting finding is that, when $K$ is small,
TRPM tends to outperform SPARE. This is because that when $K$ is small, shuffle
data of TRPM is comparable to SPARE. Meanwhile, small $K$ indicates small
size of partition in TRPM but low pruning power in SPARE. This explains the
superiority of TRPM. Note that, when $K$ is small, TRPM is 30\% 
faster than SPARE and the absolute time is less than three minutes.

\textbf{Vary $L$}:Figures~\ref{exp:performance_vary} (c)(g)(k) presents the performance
of TRPM and SPARE when $L$ changes under three datasets. We can see that $L$
provides good pruning power from $10$ to $20$ for both TRPM and SPARE. For TRPM,
the benefit of increasing $L$ is bi-folded. First, when $L$ increases from $10-50$, 
the $\eta$ decreases, which reduces the shuffle and partition sizes. Second, when
$L$ increases, the initial pruning in line-sweep is more beneficial. For SPARE,
increasing $L$ does not affect the shuffling, but benefits the simplification.
It is also observed that when $L$ increases, the pruning power increases marginally.
This is because that many patterns contains short segments, when $L$ increases,
these patterns are largely pruned.

\textbf{Vary $G$}:Figures~\ref{exp:performance_vary} (d)(h)(l) presents the performance
of TRPM and SPARE when $G$ changes under three datasets. In general, both TRPM and SPARE
runs slower when $G$ increases. This is because, when $G$ increases, exponentially more valid patterns
exist. In other words, the pruning powers in TRPM and SPARE become weaker. We notice
that there is an burst of TRPM as $G$ increases. The major reason is that 
during line-sweep, if $G$-increases, each candidate needs to wait for more time before expiring.
This makes the candidate set exponentially grows and 
the join operation becomes very expensive.
Unlike TRPM, SPARE is although affected by the increase of $G$, 
but the impact is marginal as compared
to TRPM. This is because, although true patterns may become 
exponentially large as $G$ increases, the \emph{forward closure check} of SPARE
can quickly output true patterns without enumerating every of its subset.
%\subsubsection{Effects of clusters $\epsilon$, minPt}

@@

\subsection{SPARE Analysis}
Since SPARE is superior than TRPM,
we further analyze the SPARE in terms of its power of pruning, load balance
and scalablity.

\subsubsection{Power of sequence simplification}
One of the core techniques used in SPARE is the \emph{sequence simplification} (see Section 5.2.1). 
As shown in  Algorithm~\ref{algo:apriori_mining}, we use $\mathtt{sim}(T)$
to prune false candidates. To study the power of sequence simplification,
we collect the total number of initial pairs that are pruned. The
statistics are shown in Table~\ref{tbl:pruning} under default parameters. As the table
shows, the \emph{sequence simplification} is a very powerful pruning technique.
It cuts off near 90\% of the initial pairs, which significantly reduces the costs
in Apriori Enumeration. This confirms the necessity of design such a technique.
\begin{table}[h]
\begin{tabular}{|l|c|c|c|}
\hline 
\textbf{Data Set} & \textbf{Shopping} & \textbf{Geolife} & \textbf{Taxi} \\ 
\hline 
Before pruning & 878,309 &  1,134,228 & 2,210,101 \\ 
\hline 
After pruning & 76,672 & 123,410 & 270,921 \\ 
\hline 
Prune ratio & 91.2\% & 89.1\% & 87.7\% \\ 
\hline 
\end{tabular} 
%
%\begin{tabular}{|c|c|c|c|}
%\hline 
%\textbf{Dataset} & \textbf{Initial Candidates} & \textbf{Real Candidates} & \textbf{Prune-Ratio} \\ 
%\hline 
%Shopping & 878,309 & 76,672 &  91.2\%\\ 
%\hline 
%Geolife & 1,134,228 & 123,410 & 89.1\% \\ 
%\hline 
%Taxi & 2,210,101 & 270.921 & 87.7\% \\ 
%\hline 
%\end{tabular} 
\caption{Pruning power of SPARE}
\label{tbl:pruning}
\end{table}

\subsubsection{Load Balance}
We first compare SPARE and SPARE+ by analyzing the running time at
each map-reduce stage. The detail anatomy is shown in Figure~\ref{exp:wl}(a).
We can see that for both SPARE and SPARE-LB on three datasets, the reduce 
time takes the majority. The overall improvement of SPARE-LB is around 10-13\%
under default settings. We observe that the mapping and shuffle time
of SPARE and SPARE-LB are identical, where SPARE-LB spends a very small portion 
of extra time (4\% of the total time)
in applying the best-fit strategy. The time spent is worthwhile
as in the reduce phase SPARE-LB saves around 20\% of the time. However, since 
the star sizes in SPARE is almost identical (due to Theorem~2), the best-fit
strategy does not win too much.

>>>>

\section{Experimental Study}
\label{sec:exp}
In this section, we present our experimental findings on
deploying our GCMP detectors to large-scaled real trajectories.
All the experiments are carried out on our in-house cluster: Dianwei. The cluster includes 12 nodes, each of which is equipped with four quad-core 2.2GHz Intel processors, 32 GB memory and gigabit Ethernet. The cluster is installed with CentOS 5.5. operating system.

\textbf{Environment Setup}: We use Yarn\footnote{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html}
to manage our cluster. One node is dedicated as Yarn's master node, and each other node reserves one core and 2 GB memory for
Yarn processes. We use Apache Spark 1.5.5~\cite{zaharia2012resilient} as the MapReduce framework. Spark takes
the remaining 11 nodes as the computing nodes.
To fully utilize the computing power of the cluster, 
we assign each node to run five executors, each executor takes three cores and 5 GB memory. We use "yarn-cluster" mode
for Spark which randomly picks one executor to act as the Application Master. Such a configuration allows us to run 162 tasks
at the same time. We use HDFS as our storage engine with replicator factor of 1.
The summary of the configuration is as in the following table:

\begin{table} [h]
\centering
\begin{tabular}{|l|c|}
\hline 
Parameter & Value  \\ 
\hline 
Java Version & 1.7.0 \\ 
\hline 
Spark Version & 1.5.5 \\ 
\hline 
spark.driver.memory & 2GB \\ 
\hline 
spark.executor.cores & 3  \\ 
\hline 
spark.executor.instances & 54 \\ 
\hline 
spark.executor.memory & 5GB \\ 
\hline 
spark.master & yarn-cluster \\
\hline 
spark.serializer & KryoSerializer \\ 
\hline 
\end{tabular} 
\end{table}

\textbf{Datasets}: We prepare three real datasets for experiments. The details of the datasets are as follows:
\begin{itemize}
\item{Geolife}~\footnote{http://research.microsoft.com/en-us/projects/geolife/}: this dataset collects 
18,670 trajectories for passengers in Beijing over three years. The data are collected
per around 5 seconds. Each data point records a trajectory ID and the latitude/longitude information.
\item{Shopping}~\footnote{http://www.irc.atr.jp/crest2010\_HRI/ATC\_dataset/}: this dataset contains
 visitors trajectories in ATC shopping center in Osaka. The samples are taken per
 around 0.5 seconds. There are in total 13,183 trajectories. Each data point is a 
 trajectory ID with in-door coordinates.
\item{Taxi}: this dataset records 15,054 Singapore taxi trajectories over one month span. The sample 
rate is around 30 seconds. Each data point is the taxi plate with latitude/longitude information.
\end{itemize}

\textbf{Preprocessing}: We replace timestamps with global sequences for each dataset. The sequence number
$0$ is the earliest timestamp among all trajectories in a dataset. We use the sampling rate of 
each dataset as the tick of the sequence number and every data point is mapped to the nearest ticks. If
several points mapped to the same tick, they are merged by averaging the location coordinates.
For missing data within small intervals (i.e., sequence difference less than 10), 
we use linear interpolation to fill them. 
We then use DBSCAN ($\epsilon=5, minPt=10$ for GeoLife and Shopping, $\epsilon=20, minPt=10$ for Taxi)
as the clustering algorithm for preprocessing.  
Note that both our TRPM and SPARE algorithms treat the preprocessing as a black box and other
spatial clustering methods are also applicable. The clustered snapshots are stored in HDFS in $\langle t, S_t \rangle$ pair, where
$t$ is the timestamp, $S_t$ contains the clusters at snapshot $t$. 
After preprocessing, the statistics of the three datasets are presented in Table~\ref{exp:dataset}.

@@

\textbf{Parameters}: To systematically study the performance of
our algorithms, we conduct experiments on various conditions. The variables
to be tested and their value ranges are listed in Table~\ref{tbl:parameters}. 
Default values are highlighted in bold.
\begin{table}[h]
\small
\begin{tabular}{c|l|l}
\hline 
\textbf{Variables} & \textbf{Meaning} & \textbf{Values} \\ 
\hline 
M & min size of object set &  5, 10,  \textbf{15}, 20, 25 \\ 
\hline 
K & min duration & 120, 150, \textbf{180}, 210, 240 \\ 
\hline 
L & min local duration & 10, 20, \textbf{30}, 40,50 \\ 
\hline 
G & max gap & 10, 15, \textbf{20}, 25, 30 \\ 
\hline
N & number of executors & 1, 14, 24, 34, 44, \textbf{54}\\ 
\hline 
\end{tabular} 
\caption{Variables and their default values}
\label{tbl:parameters}
\end{table}

\textbf{Number of patterns under different parameters}: We first 
analyze the number of patterns exist in each dataset under different conditions. The results are presented in Figures~\ref{exp:patterns_vary}. As expected, the number of patterns differs under in different scenarios. Larger $M$, $L$, $K$ imply smaller number of patterns, because lesser patterns are able to meet stricter $M$, $L$, $K$ constraints. In contrast, larger $G$ implies larger number of patterns. This is because larger gaps relaxes the pattern constraint. Two interesting observations are made on $L$ and $G$.
First, as $L$ increases from $10$ to $20$, the number of patterns drops quickly (50\% less). Second, opposed to $L$'s trend, as $G$ reaches to $30$ from $25$, the number of patterns bursts (near 50\% more). The distribution of patterns under $G$ and $L$ reveals that there are many companions in real life which are short and intermittent. With GCMP, we can discover these patterns by adjusting property $L$ and $G$s.

\begin{figure}[h]
\centering
 	 \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_M.eps}
        \caption{Number of patterns vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_K.eps}
        \caption{Number of patterns vary $K$}
    \end{subfigure}  
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_L.eps}
        \caption{Number of patterns vary $L$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_G.eps}
        \caption{Number of patterns vary $G$}
    \end{subfigure}    
\caption{Number of patterns discovered from real datasets}
\label{exp:patterns_vary}
\end{figure}

\textbf{Algorithms}: We implement TRPM, SPARE and SPARE-LB for comparison study. TRPM and SPARE are implement as described in Section 4 and 5. SPARE-LB extends SPARE by appending an additional load balance stage to the map phase. 
When the mappers complete, SPARE-LB collects the size of stars from all mappers. 
Then a best-fit strategy is applied for task allocation. In best-fit, 
tasks are assigned in decreasing order of their sizes, and the most costly
unassigned task is allocated to the current mostly empty reducer. 
In SPARE-LB, we simply use the number of edges in stars as a cost estimation. The other
part of SPARE-LB is identical with SPARE.

@@

\subsection{Performance Comparison}
Since the both TRPM and SPARE utilizes pruning rules that related to the pattern parameters $M$,$K$,$L$,$G$. It is interesting to
see their performances under different settings.
We run the three algorithms using all three datasets 
and report their overall performances in Figures~\ref{exp:performance_vary}.
In brief, all of the three algorithms 
are able to handle the large-scaled real
datasets. However, SPARE algorithms are obviously more efficient than TRPM. 
In the case when $G$ is large (i.e., $G=30$), 
TRMP takes near three hours for Taxi dataset, which is 15 times slower than SPARE algorithms. Besides, SPARE-LB is consistently more efficient than SPARE, with an average of 20\% improvements.
Another general observation
is that all of the three algorithms run slower in the Taxi dataset as compared to
other two datasets. This is because Taxi dataset contains
the most number of temporal data points, which is around 7 times of Shopping
dataset and 5 times of geolife dataset.
 In summary, SPARE outperforms TRMP in all cases. Next, we analyze the details of each experiments.

@@

    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_M.eps}
        \caption{Taxi vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_K.eps}
        \caption{Taxi vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_L.eps}
        \caption{Taxi vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_G.eps}
        \caption{Taxi vary $G$}
    \end{subfigure}       
\caption{Performance of SPARE and TRPM on real datasets under different pattern parameters.}
\label{exp:performance_vary}
\end{figure*}
%\subsubsection{Effects of pattern parameters M,L,K,G}
\textbf{Vary $M$}: Figures~\ref{exp:performance_vary} (a),(e),(i)
present the performance when $M$ changes.
As the figures show, SPARE based algorithms runs much faster than TRPM. We can see that SPARE
speeds up TRPM 2.7 times in Shopping data, 3.1 times in Geolife data and
7 times in Taxi data. An interesting observation is that, the running times
of all algorithms slightly decrease as $M$ grows. This is
because when $M$ becomes bigger, smaller clusters or stars can be directly pruned, which brings in the efficiency.

\textbf{Vary $K$}: Figure~\ref{exp:performance_vary} (b),(f),(j) 
presents the performances when $K$ changes. 
There are two interesting findings. 
First, SPARE based algorithms and TRPM takes different trends as $K$ increases. 
When $K$ increases, SPARE and SPARE-LB tends to run faster
while TRPM continuously slows down. For SPARE, the trends are resulted from more pruning powers brought
by $K$. When $K$ increases, more sequences can be pruned by the \emph{sequence simplification}.
Conversely, TRPM fails to utilize $K$ for pruning. Moreover, as $K$ increases, $\eta$ in TRPM grows, indicating more replication of snapshots. 
This explains the low performance of TRPM.  Second, when $K$ is small (i.e, $K$=120), TRPM could outperform SPARE. This is because smaller $K$ indicates small partition size in TRPM but restricted the pruning power in SPARE. As a result, TRPM wins 10\% in Geolife dataset. However, by leveraging the load balancing, SPARE-LB is still faster than TRPM.

\textbf{Vary $L$}: Figures~\ref{exp:performance_vary} (c)(g)(k) presents the performances when $L$ changes. We can see that SPARE based algorithms are still superior than TRPM, where SPARE-LB outperforms TRPM near 10 times when $L =10$.
An interesting observation is that $L$
provides good pruning power from $10$ to $20$ for both TRPM and SPARE based algorithms. The major reason is that the decrease of $L$ invalidates many candidates (as shown in Figure~\ref{exp:patterns_vary} (c)), thus the prunings in both SPARE and TRPM become more significant.  As $L$ continues to increase, we can see that TRPM's performance gain is larger than SPARE based algorithms. This is because larger $L$ indicates smaller $\eta$, which is more beneficial to TRPM.

\textbf{Vary $G$}: Figures~\ref{exp:performance_vary} (d)(h)(l) presents the performances when $G$ changes.  Unlike other cases, when $G$ increases, both TRPM and SPARE based algorithms run slower. The reason is that large $G$ relaxes the constraint of a pattern, thus the pruning powers of TRPM and SPARE is more restricted. We observe that there is a burst in performance of TRPM when $G$ reach to $30$. The major reason is that when $G$ becomes to 30, the number of valid patterns almost doubles as shown in Figure~\ref{exp:patterns_vary} (d). This indicate that during TRPM's line sweep, very few patterns can be pruned, making the candidate set grows exponentially. Similarly, SPARE algorithms are also affected by the increase of $G$. However we do not observe such a burst for SPARE. The reason is bi-folded. First, SPARE can utilize $K$, $L$ to retain the power of pruning. Second, SPARE leverages \emph{forward closure check} to quickly output valid patterns and avoids to enumerating many candidates.
%
%
% However, since SPARE algorithms are able to utilize $K$, $L$, $M$ in pruning, the 
%
%
%In general, both TRPM and SPARE
%runs slower when $G$ increases. This is because, when $G$ increases, exponentially more valid patterns
%exist. In other words, the pruning powers in TRPM and SPARE become weaker. We notice
%that there is an burst of TRPM as $G$ increases. The major reason is that 
%during line-sweep, if $G$-increases, each candidate needs to wait for more time before expiring.
%This makes the candidate set exponentially grows and 
%the join operation becomes very expensive.
%Unlike TRPM, SPARE is although affected by the increase of $G$, 
%but the impact is marginal as compared
%to TRPM. This is because, although true patterns may become 
%exponentially large as $G$ increases, the \emph{forward closure check} of SPARE
%can quickly output true patterns without enumerating every of its subset.
%\subsubsection{Effects of clusters $\epsilon$, minPt}

@@

\subsection{Analysis of SPARE and SPARE-LB}
As SPARE based algorithms are superior than TRPM,
we further analyze several more aspects of SPARE namely, \emph{power of pruning}, \emph{load balance} and \emph{scalability}.

\subsubsection{Power of sequence simplification}
One of the core techniques used in SPARE is the \emph{sequence simplification} (see Section 5.2.1). 
As shown in  Algorithm~\ref{algo:apriori_mining}, we use $\mathtt{sim}(T)$
to prune false candidates. To study the power of sequence simplification,
we collect the total number of pairs that are pruned before apriori enumeration. The
statistics are shown in Table~\ref{tbl:pruning} under default parameters. The result states that the \emph{sequence simplification} is a very powerful pruning technique. It cuts off near 90\% of the initial pairs, which significantly reduces the costs
of later enumerations. This confirms the necessity and usefulness of design such a technique.

\begin{table}[h]
\begin{tabular}{|l|c|c|c|}
\hline 
\textbf{Data Set} & \textbf{Shopping} & \textbf{Geolife} & \textbf{Taxi} \\ 
\hline 
Before pruning & 878,309 &  1,134,228 & 2,210,101 \\ 
\hline 
After pruning & 76,672 & 123,410 & 270,921 \\ 
\hline 
Prune ratio & 91.2\% & 89.1\% & 87.7\% \\ 
\hline 
\end{tabular} 
%
%\begin{tabular}{|c|c|c|c|}
%\hline 
%\textbf{Dataset} & \textbf{Initial Candidates} & \textbf{Real Candidates} & \textbf{Prune-Ratio} \\ 
%\hline 
%Shopping & 878,309 & 76,672 &  91.2\%\\ 
%\hline 
%Geolife & 1,134,228 & 123,410 & 89.1\% \\ 
%\hline 
%Taxi & 2,210,101 & 270.921 & 87.7\% \\ 
%\hline 
%\end{tabular} 
\caption{Pruning power of SPARE}
\label{tbl:pruning}
\end{table}

\begin{figure}[h]
\centering
	\begin{subfigure}[b]{0.22\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/detail.eps}
        \caption{Decomposed running time}
    \end{subfigure}
 	 \begin{subfigure}[b]{0.22\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/wl-shopping.eps}
        \caption{Workload in Shopping}
    \end{subfigure}
    \begin{subfigure}[b]{0.22\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/wl-geolife.eps}
        \caption{Workload in Geolife}
    \end{subfigure}  
    \begin{subfigure}[b]{0.22\textwidth}
        \includegraphics[width=\textwidth]{/exp/spare/wl-taxi.eps}
        \caption{Workload in Taxi}
    \end{subfigure}
\caption{Load balance of SPARE and SPARE-LB}
\label{exp:wl}
\end{figure}
